The Astropy Project: Building an open-science project and status of the v2.0 core package

### 2018-03-12 response.txt

> There are some stylistic issues with the text. I have left comments inline
>  where appropriate.

We have addressed all of the stylistic issues that were raised by the referee.
Here are some responses to the more detailed comments:

Comment on styles:
As it was not related to the section, we removed the first paragraph 
in the APE section that commented on different styles.  However, we
did add a comment in the affiliated package section indicating that
they may have different requirements and structure than the core package.

Comment on NDData:
At the time of initial development, the developers were not aware of 
any open source packages that would have fit the requirements of NDData.  Since
then, we have been working with different groups (LSST, sunpy) to coordinate
development of the NDData interface as well as assessing other attempts at 
something similar.  There is currently an APE about this under 
discussion (https://github.com/astropy/astropy-APEs/pull/14)  .

### 2018-03-12 response.txt

Comment on styles:
As it was not related to the section, we removed the first paragraph 
in the APE section that commented on different styles.  However, we
did add a comment in the affiliated package section indicating that
they may have different requirements and structure than the core package.

Comment on NDData:
At the time of initial development, the developers were not aware of 
any open source packages that would have fit the requirements of NDData.  Since
then, we have been working with different groups (LSST, sunpy) to coordinate
development of the NDData interface as well as assessing other attempts at 
something similar.  There is currently an APE about this under 
discussion (https://github.com/astropy/astropy-APEs/pull/14)  .

> More generally, given the technical nature of the work being described here,
> I frequently found myself wanting a small code snippet that demonstrated the
> new/improved functionality of the packages being described. Perhaps the
> authors could find a way to include short code examples where appropriate,
> either inline in the paper body or in the appendix.

We did include code snippets in the first astropy paper from 2013, and
it is not much work; we could use the same scripts to provide nicely
formatted code examples with appropriate syntax highlighting here. However,
we have made a conscious decision to avoid that this time as far as
possible. We will explain our reasoning below, but if the referee
insists, we can quickly add a few examples in a second revision.

The main reasons why we chose NOT to include code samples are:

- While we aim for stability, many of the newsest features are still
  considered provisional, meaning that their API can still change. The
  paper describes astropy 2.0, but at the time of writing this,
  astropy 3.0 is already released. We hope that this paper is useful
  for years to come. Code examples for a specific version are at risk
  of being outdated much sooner than that.

- Code examples belong in the documentation. In the documentation at
  cods.astropy.org we provide extensive examples with enough comments
  to actually understand what is going on. If readers are curious, we
  want them to read the documentation.

- It takes a lot of space to explain a code example well. Currently,
  the text lists the names of the most important classes or
  functions. To give a meaningful example that shows these classes in
  action and is useful to people not familiar with astropy (or even
  Python), we would have to detail several parameters and the format
  of the results. We think that it is more useful to explain the
  general concept in the paper and not the names and the specific
  implementation of the functions and parameters.

- Most new features would require some setup. For example, showing the
  code for WCS axis plotting is not very useful without loading an
  image with a WCS in it first. More complex features profit more from
  code examples, but they also require much more setup to make such an
  example self-consistent and useful. Again, the documentation is a better
  place for that.

As a compromise, we have added links to the documentation in many places and
there is a link in the introduction that points to the github repository where
this article is written. That repository contains (and the text in the
introduction says this) the scripts that we used to generate the figures.

### 2018-03-12 main.tex
update suggested edits
adding more edits

The \astropy Project aims to provide an open-source and open-development core
package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
support astronomical functionality in the \python programming language.
The \astropypkg core package is now a feature-rich library of sufficiently
general tools and classes that supports the development of more specialized
code. An example of such functionality is reading and writing FITS files: It would be
time consuming and impractical for multiple groups to implement the FITS
standard \citep{FITS} and maintain software for such a general-purpose need.
Another example of such a common task is in dealing with representations of and
transformations between astronomical coordinate systems.

@@

\subsection{Astropy development model}

Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github\footnote{\url{https://github.com/astropy/astropy/}})
that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before they are merged into
the core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution},
\url{http://docs.astropy.org/en/latest/development/workflow/development_workflow.html}}

@@

\subsection{APEs - Astropy Proposals for Enhancement}

@@

Affiliated packages contain functionality that is more specialized,
have license incompatibilities, or have external dependencies (e.g., GUI
libraries) that make these packages more suitable to be separate from the
\astropypkg core package.
Affiliated packages may also be used to develop substantial new functionality
that will eventually be incorporated into the \astropypkg core package
(e.g., \astropywcsaxes).
New functionality benefits from having a rapid development and release cycle 
that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).  
These projects may also have less stringent requirements for style, testing, or
development as the core package.

@@

>>>>>>> 0a5c93ffa551be5fd4bba22f4be705f8d79a39bd

>>>>

The \astropy Project aims to provide an open-source and open-development core
package (\astropypkg) and an ecosystem of \emph{affiliated packages} that
support astronomical functionality in the \python programming language.
``Open development'' describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes, or other code changes, governance, or any other aspect of the development process is discussed (see Sect.~\ref{sect:devmod} and \ref{sect:ape} of how this is organized in practice).
The \astropypkg core package is now a feature-rich library of sufficiently
general tools and classes that supports the development of more specialized
code. An example of such functionality is reading and writing FITS files: It would be
time consuming and impractical for multiple groups to implement the FITS
standard \citep{FITS} and maintain software for such a general-purpose need.
Another example of such a common task is in dealing with representations of and
transformations between astronomical coordinate systems.

@@

\subsection{Astropy development model}
\label{sect:devmod}
Code is contributed to the \astropypkg core package or modified through ``pull
requests'' (via \github\footnote{\url{https://github.com/astropy/astropy/}})
that often contain several \texttt{git} commits.
Pull requests may fix bugs, implement new features, or improve or modify the
infrastructure that supports the development and maintenance of the package.
Individual pull requests are generally limited to a single conceptual addition
or modification to make code review tractable.
Pull requests that modify or add code to a specific subpackage must be reviewed
and approved by one of the subpackage maintainers before they are merged into
the core codebase.
Bugs and feature requests are reported via the \github issue tracker and labeled
with a set of possible labels that help classify and organize the issues.
The development workflow is detailed in the \astropypkg
documentation.\footnote{\emph{How to make a code contribution},
\url{http://docs.astropy.org/en/latest/development/workflow/development_workflow.html}}

@@

\subsection{APEs - Astropy Proposals for Enhancement}
\label{sect:ape}

@@

Affiliated packages contain functionality that is more specialized,
have license incompatibilities, or have external dependencies (e.g., GUI
libraries) that make these packages more suitable to be separate from the
\astropypkg core package.
Affiliated packages may also be used to develop substantial new functionality
that will eventually be incorporated into the \astropypkg core package
(e.g., \astropywcsaxes).
New functionality benefits from having a rapid development and release cycle 
that is not tied to that of the \astropypkg core (\sectionname~\ref{sect:releasecycle}).  
These projects may also have less stringent requirements for style, testing, or
development as compared to the core package.

@@
